Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-06-17 WSSSPE3/report/WSSSPE3_review.tex
changing word in abstract
fixing a typo

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). The report includes a
description of the keynote presentation of the workshop, which served as an overview of sustainable
scientific software. It also summarizes a set of lightning
talks in which speakers highlighted to-the-point lessons and challenges
pertaining to sustaining scientific software. The final and main contribution of the report is a summary of the
discussions, future steps, and future organization for a set of self-organized
working groups on topics including developing pathways to funding scientific
software; constructing useful common metrics for crediting software
stakeholders; identifying principles for sustainable software engineering
design; reaching out to research software organizations around the world; and
building communities for software sustainability. For each group, we include a
point of contact and a landing page that can be used by those who want to join
that group's future activities. The main challenge left by the workshop is to
see if the groups will execute these activities that they have scheduled, and
how the WSSSPE community can encourage this to happen.

@@

WSSSPE3 also included two professional
event organizers/facilitators from Knowinnovation who helped the organizing committee members
plan the workshop agenda, and during the workshop, they actively engaged
participants with variously
tools, activities, and reminders.

>>>>

\begin{abstract}
This report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). The report includes a
description of the keynote presentation of the workshop, which served as an overview of sustainable
scientific software. It also summarizes a set of lightning
talks in which speakers highlighted to-the-point lessons and challenges
pertaining to sustaining scientific software. The final and main contribution of the report is a summary of the
discussions, future steps, and future organization for a set of self-organized
working groups on topics including developing pathways to funding scientific
software; constructing useful common metrics for crediting software
stakeholders; identifying principles for sustainable software engineering
design; reaching out to research software organizations around the world; and
building communities for software sustainability. For each group, we include a
point of contact and a landing page that can be used by those who want to join
that group's future activities. The main challenge left by the workshop is to
see if the groups will execute these activities that they have scheduled, and
how the WSSSPE community can encourage this to happen.

@@

WSSSPE3 also included two professional
event organizers/facilitators from Knowinnovation who helped the organizing committee members
plan the workshop agenda, and during the workshop, they actively engaged
participants with various
tools, activities, and reminders.
